---
title: 'Bayes: MC integration to MCMC'
header-includes:
  - \usepackage[fleqn]{amsmath}
output: html_document

---
  

>  Bayesian      and       frequentist methods  

> Data: $X$        Parameters: $\Theta$



#### Frequentist

* The data are random.  The parameters are fixed.
* ML estimation fines $\Theta$ to maximize the likelihood $f(x^{n}|\theta)$
* Cannot make probability statements about parameters.  Instead, make statements about the performance of the estimator.



#### Bayesian

* Data are fixed. Parameters are random.
* Inferences are made on the basis of the posterior $(x^{n}|\theta)$
* 



*****
######

# Bayesian Basics

Posterior is proportional to Likelihood times Prior  

$$
\begin{flalign}
f(\theta |x^{n}) &=\frac{f(x^{n}|\theta)f(\theta )}{\int f(x^{n}|\theta)f(\theta )d\theta }\\
&=\frac{\mathit{L_{n}(\theta )f(\theta )}}{c_{n}}\\
\end{flalign}
$$

where 
$$
c_{n}=\int{\mathit{L_{n}(\theta )f(\theta )}}d\theta 
$$

Posterior: $f(\theta |x^{n})$  
Prior:  $f(\theta )$  
Likelihood:  $f(x^{n}|\theta)$  










```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
